\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Yash Kulkarni} \\ \vspace{1pt}
    \small +91 9915181929 $|$ \href{mailto:yashkulkarni2008@gmail.com}{\underline{yashkulkarni2008@gmail.com}} $|$
    \href{www.linkedin.com/in/yashkulkarni08}{\underline{www.linkedin.com/in/yashkulkarni08}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {St. Mary's School}{Udupi, Karnataka}
      {Grade 12th, PCM (CS)}{Feb. 2025 -- Apr. 2026}
    \resumeSubheading
      {Chandigarh Baptist School}{Chandigarh, India}
      {Grade 11th, PCM (CS)}{Apr. 2024 -- Feb. 2025}
    \resumeSubheading
      {The Gurukul}{Chandigarh, India}
      {Grade 6th to 10th}{Apr. 2018 -- Mar. 2024}
    \resumeSubheading
      {Cambridge International School, Banglore}{Bangalore, India}
      {Grade 3rd to 6th}{Apr. 2015 -- Apr. 2018}
    \resumeSubheading
      {Hillside Academy}{India}
      {Grade 1st to 3rd}{Mar. 2013 -- Apr. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chief Executive Officer \& Founder}{Jan. 2025 -- Present}
      {PurpleRain TechSafe}{India and Los Angeles}
    \resumeSubheading
      {Co-Founder \& Chief Technology Officer}{Nov. 2024 -- Jan. 2025}
      {CodeQuestt Hackathon}{Chandigarh, India}
      \resumeItemListStart
        \resumeItem{Oversee organizing hackathons designed to foster innovation and creativity in students and developers.}
        \resumeItem{Planning, managing collaborations with schools and professionals, and handling partnerships to create impactful experiences for participants.}
      \resumeItemListEnd
    \resumeSubheading
      {Co-Founder}{June 2024 -- Jan. 2025}
      {CodeQuestt Hackathon}{Chandigarh, India}
    \resumeSubheading
      {Development Volunteer}{Jan. 2023 -- Dec. 2024}
      {Trace Labs}{Chandigarh, India}
      \resumeItemListStart
        \resumeItem{Actively involved in using OSINT (Open Source Intelligence) to assist in locating missing persons.}
        \resumeItem{Gathering and analyzing publicly available data to generate actionable leads, collaborating with a global team of volunteers, and participating in Capture the Flag (CTF) events to enhance our search efforts.}
        \resumeItem{Honing investigative and analytical skills and contributing to a cause that aims to reunite families and provide closure to those in need.}
      \resumeItemListEnd
    \resumeSubheading
      {Web Development UI\/UX}{July 2024}
      {Zimmer Biomet}{}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, HTML\/CSS} \\
     \textbf{Frameworks}{: } \\
     \textbf{Developer Tools}{: } \\
     \textbf{Libraries}{: }
    }}
 \end{itemize}

%-----------AWARDS-----------
\section{Awards}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Special Invite to a Seminar Session on Ethical Hacking at IIT Delhi}{ 2024} \\
     \textbf{First Place at C.O.D.E. Hack 2023}{ 2023, Strawberry Fields High School} \\
     \textbf{Best Personal Website Design 2024}{ 2024, International Web Developers' Summit}
    }}
 \end{itemize}

%-----------LEADERSHIP-----------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Co-Founder \& Chief Technology Officer}{Nov. 2024 -- Jan. 2025}
      {CodeQuestt Hackathon}{Chandigarh, India}
      \resumeItemListStart
        \resumeItem{Oversee organizing hackathons designed to foster innovation and creativity in students and developers.}
        \resumeItem{Planning, managing collaborations with schools and professionals, and handling partnerships to create impactful experiences for participants.}
      \resumeItemListEnd
    \resumeSubheading
      {Leader}{}
      {CypherSec}{}
  \resumeSubHeadingListEnd

%-----------OTHER-----------
\section{Other}
  \resumeSubHeadingListStart
    \resumeItem{Working with Trace Labs NGO, to find missing people via strategic investigation.}
    \resumeItem{Co-Founder and Host, CodeQuestt Hackathon.}
    \resumeItem{Swimming}
    \resumeItem{Roller Skating}
    \resumeItem{Delegation}
    \resumeItem{Hindi (Full Professional)}
    \resumeItem{Punjabi (Professional Working)}
    \resumeItem{Marathi (Native or Bilingual)}
    \resumeItem{Kannada (Elementary)}
    \resumeItem{English (Native or Bilingual)}
    \resumeItem{German (Elementary)}
    \resumeItem{Avid chess player and debater}
    \resumeItem{Playing the keyboard, practicing MMA, and participating in Model United Nations (MUN) conferences}
  \resumeSubHeadingListEnd

\end{document}
